|

### 2022-11-15 paper_comparison/paper_comparison/paper_comparison.Rmd
update distribution cmp

## Distribution of regressor

The impact of the distribution of $X_raw$ on the power is displayed in Figure \ref{fig:dist-power}. The power curve of F-test is stable across different distributions, while the visual test has a steeper power curve for normal and uniform distribution. BP-test performs worse for discrete uniform distribution and uniform distribution but has relatively high power for normal distribution. SW-test outperforms BP-test for discrete uniform distribution but remains as the worst test for other distributions. The results indicate those inappropriate residual-based tests are sensitive to the distribution of the regressor.

@@

```{r dist-power, fig.cap="..."}
vi_survey %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "polynomial") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
                bind_rows(mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "heteroskedasticity") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist))), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_grid(x_dist~type)
```

<!-- ## Power comparison -->

<!-- ### Experiment I -->

<!-- Figure \ref{fig:power-overview} shows an overview of estimated power of visual test against natural logarithm of the effect with comparison to the power of an exact test - F-test, and the power of two other residual-based conventional tests commonly used in regression diagnostics but for testing other departures from the model assumptions. In overall, the power of all four tests increases as the effect becomes larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while others respond inactively to the change of effect and remain lower than 25% throughout the period, showing that as an exact test, the F-test is relatively more sensitive to the type of model defects that being considered. The power of visual test arises steadily and nearly linearly to around 90% as $log_e(E)$ increases from 2 to 5, suggesting that the effect starts to make noticeable impact on the degree of the presence of the designed visual features. Other two inappropriate conventional tests shows improvement at the same time but at a lower rate. This coincides the point made by @cook1982residuals mentioned in \ref{hypothesis-testing} that residual-based tests for a specific type of model defect are sensitive to other types of model defects. At $log_e(E) = 6$, the power curve of F-test reaches almost 100% followed by the visual test by a small margin. The power of Breusch--Pagan test and Shapiro--Wilk test reach around 75% and 63% respectively. -->

<!-- What truly impress us is the huge difference between the estimated power of visual test and the estimated power of F-test. The margin is largest at around $log_e(E) = 2$. An example lineup is included in Figure \ref{fig:power-overview} where none of subjects detect the actual data plot positioned at panel 14. It demonstrates that at this level of difficulty, the designed visual feature is rarely visible, making the actual data plot indistinguishable from residual plots simulated from the assumed model. From a communication perspective, given the fact that the visual difference is unperceivable, the argument that non-linearity present in the fitted model is less convincing to the public even though it is true. At around $log_e(E) = 3$, the margin gets smaller as the chance of identifying the actual data plot becomes larger. At this level of difficulty, the designed visual features are usually detectable but it may not stand out from the lineup as other null plots may happen to include outliers or visual patterns that are are considered to be more attractive by human, and thus recognized as the most different plot. Without knowing the designed visual features beforehand, it is actually hard to identify the actual data plot by pure image comparison. The corresponding example lineup for $log_e(E) = 3$ shown in Figure \ref{fig:power-overview} has the actual data plot positioned at panel 20, where two out of five subjects detect it. It can be observed that a M-shape is presented in plot 20, but the signal is not strong enough to attract all five subjects, resulting in a visual p-value sightly above the desired significance level $\alpha = 0.05$. At $log_e(E) = 4$ and $log_e(E) = 6$, the designed visual features become much clear and attractive, leading to a high percentage of rejection of the null hypothesis. Figure \ref{fig:power-overview} gives example lineups of such cases. -->

<!-- It is also interesting to observe that the power curve of visual test behaves similarly to those inappropriate conventional tests until the designed visual features really becomes visible   -->

<!-- ```{r} -->
<!-- conv_test_plot <- function() { -->
<!--   conv_result %>% -->
<!--   ggplot() + -->
<!--   stat_smooth(geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "F-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) + -->
<!--   stat_smooth(geom = "line",  -->
<!--               aes(log(effect_size), reject, col = "F-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1) + -->
<!--   labs(col = "Test") + -->
<!--   theme_light(base_size = 5) + -->
<!--   xlab(quote(log[e](E))) + -->
<!--   ylab("Power") -->
<!-- } -->

<!-- add_wrong_BP_conv_test_plot_layers <- function(p) { -->
<!--   p + -->
<!--   stat_smooth(data = wrong_BP_conv_result, geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "BP-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) + -->
<!--   stat_smooth(data = wrong_BP_conv_result, geom = "line",  -->
<!--               aes(log(effect_size), reject, col = "BP-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1) -->
<!-- } -->

<!-- add_wrong_SW_conv_test_plot_layers <- function(p) { -->
<!--   p + -->
<!--   stat_smooth(data = wrong_SW_conv_result, geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "SW-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) + -->
<!--   stat_smooth(data = wrong_SW_conv_result, geom = "line",  -->
<!--               aes(log(effect_size), reject, col = "SW-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- boot_dat <- function(dat, times = 100) { -->
<!--   result <- mutate(dat, boot_id = 1) -->
<!--   for (i in 2:times) { -->
<!--     result <- bind_rows(result, mutate(dat[sample(1:nrow(dat), replace = TRUE), ], boot_id = i))  -->
<!--   } -->
<!--   result -->
<!-- } -->

<!-- add_visual_test_plot_layers <- function(p, points = c()) { -->
<!--   visual_dat <- polynomials %>% -->
<!--   group_by(lineup_id) %>% -->
<!--   summarise(across(c(type:p_value, prop_detect), first)) %>% -->
<!--   filter(lineup_id < 577) %>% -->
<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->
<!--   boot_dat(times = 100) -->

<!--   p + -->
<!--   stat_smooth(data = filter(visual_dat, boot_id == 1), geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "Visual"),  -->
<!--               method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 1) + -->
<!--   stat_smooth(data = visual_dat, geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "Visual"),  -->
<!--               method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 0.05) + -->
<!--   geom_point(data = filter(visual_dat, boot_id == 1), aes(log(effect_size), prop_detect), alpha = 0.1) +  -->
<!--   geom_point(data = filter(visual_dat, boot_id == 1, lineup_id %in% points), aes(log(effect_size), prop_detect), alpha = 1, col = "red", size = 2) -->
<!-- } -->

<!-- control_col <- function(p, ...) { -->
<!--   p + scale_color_manual(values = unlist(list(...))) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r eval = FALSE} -->
<!-- filter(polynomials, lineup_id == 131) -->

<!-- polynomials %>% -->
<!--   group_by(lineup_id) %>% -->
<!--   summarise(dd = first(abs(log(effect_size) - 5)), p_value = first(p_value), prop_detect = first(prop_detect)) %>% -->
<!--   arrange(dd) %>% -->
<!--   head(30) %>% -->
<!--   summarise(tt = median(prop_detect)) -->

<!-- polynomials %>% -->
<!--   ggplot() + -->
<!--   geom_point(aes(prop_detect, p_value < 0.06)) -->

<!-- bottom_plot_2 -->

<!-- polynomials %>% -->
<!--   filter(lineup_id == 364) -->

<!-- polynomials %>% -->
<!--   filter(e_sigma == 4) %>% -->
<!--   group_by(lineup_id) %>% -->
<!--   summarise(p_value = first(p_value)) %>% -->
<!--   mutate(reject = p_value < 0.05) %>% -->
<!--   {mean(.$reject)} -->

<!-- 4 * 4 * 3 * 5 -->
<!-- ``` -->

<!-- ```{r power-overview, fig.height=7.5, fig.cap="Power overview. \\label{fig:power-overview}"} -->
<!-- conv_test_plot() %>% -->
<!--   add_wrong_BP_conv_test_plot_layers() %>% -->
<!--   add_wrong_SW_conv_test_plot_layers() %>% -->
<!--   add_visual_test_plot_layers(points = c(415, 131, 322, 378)) + -->
<!--   geom_vline(xintercept = 2, linetype = 2) +  -->
<!--   geom_vline(xintercept = 3, linetype = 2) + -->
<!--   geom_vline(xintercept = 4, linetype = 2) + -->
<!--   geom_vline(xintercept = 5, linetype = 2) -> base_plot -->

<!-- # VI_MODEL$plot_lineup(polynomials_lineup$lineup_314$data, -->
<!-- #                      size = 0.1, -->
<!-- #                      stroke = 0.2, -->
<!-- #                      remove_grid_line = TRUE, -->
<!-- #                      theme = theme_light(base_size = 5), -->
<!-- #                      remove_axis = TRUE) + -->
<!-- #   ggtitle(bquote(log[e](E) == 0~", F-test p-value" == .(format(filter(polynomials, lineup_id == 314)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 314)$p_value[1], digits = 3)))) -> bottom_plot_1 -->

<!-- VI_MODEL$plot_lineup(polynomials_lineup$lineup_415$data, -->
<!--                      size = 0.1, -->
<!--                      stroke = 0.2, -->
<!--                      remove_grid_line = TRUE, -->
<!--                      theme = theme_light(base_size = 5), -->
<!--                      remove_axis = TRUE) + -->
<!--   ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 415)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 415)$p_value[1], digits = 3)))) -> bottom_plot_1 -->

<!-- VI_MODEL$plot_lineup(polynomials_lineup$lineup_131$data, -->
<!--                      size = 0.1, -->
<!--                      stroke = 0.2, -->
<!--                      remove_grid_line = TRUE, -->
<!--                      theme = theme_light(base_size = 5), -->
<!--                      remove_axis = TRUE) + -->
<!--   ggtitle(bquote(log[e](E) %~~% 3~", F-test p-value" == .(format(filter(polynomials, lineup_id == 131)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 131)$p_value[1], digits = 3)))) -> bottom_plot_2 -->

<!-- VI_MODEL$plot_lineup(polynomials_lineup$lineup_322$data, -->
<!--                      size = 0.1, -->
<!--                      stroke = 0.2, -->
<!--                      remove_grid_line = TRUE, -->
<!--                      theme = theme_light(base_size = 5), -->
<!--                      remove_axis = TRUE) + -->
<!--   ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 322)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 322)$p_value[1], digits = 3)))) -> bottom_plot_3 -->

<!-- VI_MODEL$plot_lineup(polynomials_lineup$lineup_378$data, -->
<!--                      size = 0.1, -->
<!--                      stroke = 0.2, -->
<!--                      remove_grid_line = TRUE, -->
<!--                      theme = theme_light(base_size = 5), -->
<!--                      remove_axis = TRUE) + -->
<!--   ggtitle(bquote(log[e](E) %~~% 5~","~"F-test p-value" == .(format(filter(polynomials, lineup_id == 378)$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(polynomials, lineup_id == 378)$p_value[1], digits = 3)))) -> bottom_plot_4 -->

<!-- design <- c(patchwork::area(1, 1, 1, 8),  -->
<!--             patchwork::area(2, 1, 2, 4),  -->
<!--             patchwork::area(2, 5, 2, 8),  -->
<!--             patchwork::area(3, 1, 3, 4),  -->
<!--             patchwork::area(3, 5, 3, 8)) -->

<!-- patchwork::wrap_plots(base_plot, B = bottom_plot_1, C = bottom_plot_2, D = bottom_plot_3, E = bottom_plot_4, design = design) -->
<!-- ``` -->

<!-- ### Distributions of regressor -->

<!-- The impact of the distribution of $X_raw$ on the power is shown in Figure \ref{fig:dist-power}. The power curve of F-test is stable across different distributions, while the visual test has a steeper power curve for normal and uniform distribution. BP-test performs worse for discrete uniform distribution and uniform distribution but has relatively high power for normal distribution. SW-test outperforms BP-test for discrete uniform distribution but remains as the worst test for other distributions. The results indicate those inappropriate residual-based tests are sensitive to the distribution of the regressor. -->

<!-- ```{r dist-power, fig.cap="\\label{dist-power}"} -->
<!-- conv_test_plot() %>% -->
<!--   add_wrong_BP_conv_test_plot_layers() %>% -->
<!--   add_wrong_SW_conv_test_plot_layers() %>% -->
<!--   add_visual_test_plot_layers() + -->
<!--   facet_wrap(~x_dist) -->
<!-- ``` -->

<!-- #### Shpaes of non-linearity -->

<!-- Figure \ref{fig:shape-power} illustrates the change of power under different shape of non-linearity. Similar to the power curves shown in \ref{fig:dist-power}, F-test is stable under different shapes. The power curve of visual test also behaves similarly across different shapes. What vary are the power curve of BP-test and SW-test. For Triple-U shape, both BP-test and SW-test are insensitive to the change of the effect. And for W shape, both tests have almost identical power curves. It can be observed that both tests performs the best for U-shape. -->

<!-- ```{r shape-power, fig.cap="\\label{shape-power}"} -->
<!-- conv_test_plot() %>% -->
<!--   add_wrong_BP_conv_test_plot_layers() %>% -->
<!--   add_wrong_SW_conv_test_plot_layers() %>% -->
<!--   add_visual_test_plot_layers() + -->
<!--   facet_wrap(~shape) -->
<!-- ``` -->

<!-- ```{r eval = FALSE} -->
<!-- conv_test_plot() %>% -->
<!--   add_wrong_BP_conv_test_plot_layers() %>% -->
<!--   add_wrong_SW_conv_test_plot_layers() %>% -->
<!--   add_visual_test_plot_layers() + -->
<!--   facet_wrap(~e_sigma) -->
<!-- ``` -->

<!-- #### Reasons for making selections -->

<!-- ```{r} -->
<!-- polynomials %>% -->
<!--   mutate(reason_tmp = ifelse(reason %in% c("Cluster(s)", "Shape", "Outlier(s)"), reason, "Other")) %>% -->
<!--   ggplot() + -->
<!--   geom_bar(aes(reason_tmp)) + -->
<!--   facet_grid(x_dist~detect)  -->
<!-- ``` -->

<!-- ### Experiment II -->

<!-- <!-- todo: check the two way interaction for x_dist and a --> -->

<!-- ```{r eval = FALSE} -->
<!-- heter %>% -->
<!--   filter(b < 3) %>% -->
<!--   group_by(lineup_id) %>% -->
<!--   summarise(p_value = first(p_value), n_eval = n()) %>% -->
<!--   filter(n_eval > 3) %>% -->
<!--   mutate(reject = p_value < 0.05) %>% -->
<!--   {mean(.$reject)} -->

<!-- ``` -->

<!-- ```{r} -->
<!-- map_to_group <- function(b) { -->
<!--   round(b / 4) + 1 -->
<!-- } -->

<!-- heter_conv_test_plot <- function() { -->
<!--   conv_result_heter %>% -->
<!--   mutate(cat_b = map_to_group(b)) %>% -->
<!--   ggplot() + -->
<!--   stat_smooth(geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "BP-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) + -->
<!--   stat_smooth(geom = "line",  -->
<!--               aes(log(effect_size), reject, col = "BP-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1) + -->
<!--   labs(col = "Test") + -->
<!--   theme_light(base_size = 5) + -->
<!--   xlab(quote(log[e](E))) + -->
<!--   ylab("Power") -->
<!-- } -->

<!-- add_heter_SW_plot_layers <- function(p) { -->
<!--   p + -->
<!--   stat_smooth(data = mutate(conv_result_heter_SW, cat_b = map_to_group(b)), geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "SW-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 0.05) + -->
<!--   stat_smooth(data = mutate(conv_result_heter_SW, cat_b = map_to_group(b)), geom = "line",  -->
<!--               aes(log(effect_size), reject, col = "SW-test"),  -->
<!--               se = FALSE, method = "glm", method.args = list(family = binomial()), alpha = 1) -->
<!-- } -->

<!-- add_heter_visual_test_plot_layers <- function(p, points = c()) { -->

<!--   visual_dat <- heter %>% -->
<!--   mutate(x_dist = ifelse(x_dist == "discrete_uniform", "even_discrete", x_dist)) %>% -->
<!--   mutate(x_dist = ifelse(x_dist == "neglognormal", "lognormal", x_dist)) %>% -->
<!--   group_by(lineup_id) %>% -->
<!--   summarise(across(c(type:p_value, prop_detect), first)) %>% -->
<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->
<!--   boot_dat(times = 100) %>% -->
<!--   mutate(cat_b = map_to_group(b)) -->

<!--   p + -->
<!--   stat_smooth(data = filter(visual_dat, boot_id == 1), geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "Visual"),  -->
<!--               method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 1) + -->
<!--   stat_smooth(data = visual_dat, geom = "line",  -->
<!--               aes(log(effect_size), reject, group = boot_id, col = "Visual"),  -->
<!--               method = "glm", method.args = list(family = binomial), se = FALSE, alpha = 0.05) + -->
<!--   geom_point(data = filter(visual_dat, boot_id == 1), aes(log(effect_size), prop_detect), alpha = 0.1) +  -->
<!--   geom_point(data = filter(visual_dat, boot_id == 1, lineup_id %in% points), aes(log(effect_size), prop_detect), alpha = 1, col = "red", size = 2) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r} -->
<!-- heter_conv_test_plot() %>% -->
<!--   add_heter_SW_plot_layers() %>% -->
<!--   add_heter_visual_test_plot_layers() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- heter_conv_test_plot() %>% -->
<!--   add_heter_SW_plot_layers() %>% -->
<!--   add_heter_visual_test_plot_layers() + -->
<!--   facet_wrap(~a) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- heter_conv_test_plot() %>% -->
<!--   add_heter_SW_plot_layers() %>% -->
<!--   add_heter_visual_test_plot_layers() + -->
<!--   facet_grid(x_dist~a) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- heter_conv_test_plot() %>% -->
<!--   add_heter_SW_plot_layers() %>% -->
<!--   add_heter_visual_test_plot_layers() + -->
<!--   facet_wrap(~x_dist) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- heter_conv_test_plot() %>% -->
<!--   add_heter_SW_plot_layers() %>% -->
<!--   add_heter_visual_test_plot_layers() + -->
<!--   facet_wrap(~cat_b) -->
<!-- ``` -->

<!-- # time taken vs order of the plot -->

<!-- # accuracy vs order of the plot -->

<!-- # num of selection vs order of the plot -->

<!-- # order of the plot? -->

<!-- # summary of the demographic information -->

<!-- # Old -->

<!-- ## Overview of the Data -->

<!-- We collected 400 lineup evaluations made by 20 participants in experiment I and 880 lineup evaluations made by 44 participants in experiment II. In total, 442 unique lineups were evaluated by 64 subjects. In experiment I, one of the participants skipped all 20 lineups. Hence, the submission was rejected and removed from the dataset. In experiment II, there was a participant failed one of the two attention checks, but there was no further evidence of low-effort throughout the experiment. Therefore, the submission was kept. -->

<!-- ## Power comparision -->

<!-- 1. power (visual test vs. conventional test) -->

<!-- (visual test most different one (everything test, any departure)) -->

<!-- plot figure in a paper, desc, exp -->

<!-- 2. investigate the difference (gap), give examples -->

<!-- 3. conventional is too sensitive -->

<!-- 4. make conventional less sensitive (vary alpha) -->

<!-- To model the power of visual test, 10 logistic regression were fit for different number of evaluations ranged from one to five and two different types of simulation setting. All 10 models used natural logarithm of the effect size as the only fixed effect, and whether the test successfully rejects the null hypothesis as the response variable. Given the way we define the effect size, it was expected that with larger effect size, both conventional test and visual test will have higher probability in rejecting the null hypothesis when it is not true. The modelling result summarized in \ref{tab:powerglmcubic} and \ref{tab:powerglmheter} aligned with the expectation as the coefficients of natural logarithm of the effect size are positive and significant across all 10 models. -->

<!-- Figure \ref{fig:power-com} illustrates the fitted models, while providing the local constant estimate of the power of F-test and Breusch–Pagan test for comparison. Data for the conventional test is simulated under the model setting described in section ... and 5000000 samples are drawn for both cubic and heteroskedasticity model. From Figure \ref{fig:power-com}, it can be observed that the fitted power of visual test increased as the number of evaluations increased for both cubic and heteroskedasticity model. -->

<!-- For heteroskedasticity model, this phenomenon was more obvious as the power of visual tests with evaluations greater than two were always greater than those with evaluations smaller than two.  -->

<!-- For cubic model, the separation between curves was small. The estimated power of visual tests with three to five evaluations were almost identical to each other in regards of effect size. In addition, all five curves peaked at one as effect size increased, suggesting that identification of non-linearity as a visual task can be completed reliably by human as long as the departure from null hypothesis is large enough. -->

<!-- As shown in Figure \ref{fig:power-com}, both F-test and Breusch–Pagan test generally possessed greater power than visual test. A visual tests is a collection of test against any alternatives that would create visual discoverable features, while a conventional test is usually targeting at a pre-specified alternative. Considering the data generating process of the model defect was known and controlled in this research, where all other alternatives have been eliminated except the one we concerned, the result was suggested that conventional tests were more sensitive to violations of linearity and homoscedasticity assumption than visual tests.  -->

<!-- It was also found that there was a noticeable gap between curves of the conventional test and the visual test at around $log(\text{effect size}) = 0$ for the cubic model and $log(\text{effect size}) = 2.5$ for the heteroskedasticity model, where the differences in power were greater than 0.6. We further analysed the lineups with correspoding effect sizes. Figure \ref{fig:cubic-hard} and \ref{fig:heter-hard} showed that human was indeed hard to identify the patterns at this level of difficulty. The visual difference between the true data plot and null plots were almost unnoticeable.  -->

<!-- <!-- sample 1, change values of a and b, plot the data  -->

--\>

<!-- ## Effect of parameters on power of the visual test -->

<!-- The previous section focuses on the change of effect size relative to the power of the visual test. However, effect size is only a one dimensional summarisation of parameters used in data simulation. Individual factor embedded in the simulation process should also be analysed.  -->

<!-- In cubic model, two major factors that influencing the strength of the signal are $a$ and $b$. Figure \ref{fig:power-com-cubic-a} and \ref{fig:power-com-cubic-a} illustrates 30 different logistic regressions fit for different number of evaluations and different number of observations $n$. The regressor used in these models was $|a|/\sigma$ since the noise level $\sigma$ needed to be taken into account. From the figures, we can observe ... -->

<!-- ```{r power-vs-log-effect-size} -->

<!-- polynomials %>% -->

<!--   group_by(lineup_id) %>% -->

<!--   summarise(across(c(type:p_value), first)) %>% -->

<!--   filter(lineup_id < 577) %>% -->

<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->

<!--   ggplot() + -->

<!--   geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   xlab("Natural logarithm of effect size") + -->

<!--   ylab("Power") -->

<!-- ``` -->

<!-- ```{r power-vs-log-effect-size-given-x-dist} -->

<!-- polynomials %>% -->

<!--   group_by(lineup_id) %>% -->

<!--   summarise(across(c(type:p_value), first)) %>% -->

<!--   filter(lineup_id < 577) %>% -->

<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->

<!--   ggplot() + -->

<!--   geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   facet_wrap(~x_dist) + -->

<!--   xlab("Natural logarithm of effect size") + -->

<!--   ylab("Power") + -->

<!--   ggtitle("Power comparison conditional on the distribution of X") -->

<!-- ``` -->

<!-- ```{r power-of-visual-test-given-x-dist} -->

<!-- polynomials %>% -->

<!--   group_by(lineup_id) %>% -->

<!--   summarise(across(c(type:p_value), first)) %>% -->

<!--   filter(lineup_id < 577) %>% -->

<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->

<!--   ggplot() + -->

<!--   geom_smooth(aes(log(effect_size), reject, col = x_dist), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   xlab("Natural logarithm of effect size") + -->

<!--   ylab("Power") + -->

<!--   ggtitle("Power of visual test conditional on the distribution of X") -->

<!-- ``` -->

<!-- ```{r power-vs-log-effect-size-given-shape} -->

<!-- polynomials %>% -->

<!--   group_by(lineup_id) %>% -->

<!--   summarise(across(c(type:p_value), first)) %>% -->

<!--   filter(lineup_id < 577) %>% -->

<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->

<!--   ggplot() + -->

<!--   geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   facet_wrap(~shape) + -->

<!--   xlab("Natural logarithm of effect size") + -->

<!--   ylab("Power") + -->

<!--   ggtitle("Power comparison conditional on the shape of the Hermite polynomials") -->

<!-- ``` -->

<!-- ```{r power-of-visual-test-given-shape} -->

<!-- polynomials %>% -->

<!--   group_by(lineup_id) %>% -->

<!--   summarise(across(c(type:p_value), first)) %>% -->

<!--   filter(lineup_id < 577) %>% -->

<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01)), shape = factor(shape)) %>% -->

<!--   ggplot() + -->

<!--   geom_smooth(aes(log(effect_size), reject, col = shape), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   xlab("Natural logarithm of effect size") + -->

<!--   ylab("Power") + -->

<!--   ggtitle("Power of visual test conditional on the shape of the Hermite polynomials") -->

<!-- ``` -->

<!-- ```{r power-vs-log-effect-size-given-number-of-observations} -->

<!-- polynomials %>% -->

<!--   group_by(lineup_id) %>% -->

<!--   summarise(across(c(type:p_value), first)) %>% -->

<!--   filter(lineup_id < 577) %>% -->

<!--   mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>% -->

<!--   ggplot() + -->

<!--   geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) + -->

<!--   facet_wrap(~n) + -->

<!--   xlab("Natural logarithm of effect size") + -->

<!--   ylab("Power") + -->

<!--   ggtitle("Power comparison conditional on the number of observations") -->

<!-- ``` -->

<!-- ```{r power-of-visual-test-given-number-of-observations} -->

<!-- polynomials %>% -->

>>>>

The impact of the distribution of $X_{raw}$ on the power is displayed in Figure \ref{fig:dist-power}. For the non-linearity model, the power curve of F-test is stable across different distributions, while the visual test has a more gentle power curve for the discrete uniform distribution as it contains lineups with larger effect size. BP test performs worse for discrete uniform distribution but has relatively high power for normal distribution. SW test outperforms BP test for discrete uniform distribution but remains as the worst test for other distributions. The results indicate those inappropriate residual-based tests are sensitive to the distribution of the regressor.

For the heteroskedasticity model, F-test is entirely insensitive to the non-constant variance. The visual test has similar power as the SW test  
for normal distribution and lognormal distribution, and has higher power for uniform distribution, and lower power for discrete uniform distribution.

But still, we observe the huge gap in power between the preferred conventional tests and the visual test which is consistent with our previous argument that conventional test is too sensitive for diagnosing non-linearity and heteroskedasticity.

@@

```{r, fig.cap="..."}
vi_survey %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "polynomial") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
                bind_rows(mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "heteroskedasticity") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist))), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_grid(x_dist~type)
```

```{r}
vi_survey %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "polynomial") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist)) %>%
                bind_rows(mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)) %>%
                mutate(type = "heteroskedasticity") %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", "discrete uniform", x_dist))), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  facet_grid(shape~type)
```
